Codebook created on 2025-04-22 at 2025-04-22 13:34:49

### 2025-04-22 codebook_data_simulated.Rmd
time stampo of answering to synthetic

---
title: "Codebook created on 2025-04-03 at 2025-04-03 10:38:35"
output: github_document
---

@@

## Dataset description
The data contains 1000 cases and 27 variables.

>>>>

---
title: "Codebook created on 2025-04-22 at 2025-04-22 13:34:49"
output: github_document
---

@@

## Dataset description
The data contains 1000 cases and 28 variables.
